Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2021-08-30 article/draft.tex
add the information panel about vaccination information

To further study the assignment of information panels to videos, we compiled a list of $170$ YouTube videos, fact-checked by Science Feedback between April $2019$ and March $2021$ and marked as containing false or inaccurate information. 
We collected the information panels, when present, under each video by connecting to a US server and scraping the content of the web page. 
Five types of information panels were found regarding climate change, COVID-19 Vaccine, COVID-19, vaccine hesitancy and US elections, as shown in figure \ref{youtube_panel_screenshots}.
{\color{red} [ADD Vaccine hesitancy screenshot]}

\begin{figure}[h]
	\centering
		\includegraphics[scale=0.3]{./img/youtube_panels/yt_1.png} 
		\includegraphics[scale=0.29]{./img/youtube_panels/yt_2.png} 
		\includegraphics[scale=0.294]{./img/youtube_panels/yt_3.png}
		\includegraphics[scale=0.3]{./img/youtube_panels/yt_4.png} 
	\caption{Examples of YouTube information panels displayed under Youtube videos respectively about: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{Climate change}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{COVID-19 Vaccine}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{COVID-19} and \href{https://www.youtube.com/watch?v=8PAwc8nlE\_Q}{US elections}. The videos were accessed on July 21, 2021 from a US server.}
	\label{youtube_panel_screenshots}
\end{figure}

>>>>

To further study the assignment of information panels to videos, we compiled a list of $170$ YouTube videos, fact-checked by Science Feedback between April $2019$ and March $2021$ and marked as containing false or inaccurate information. 
We collected the information panels, when present, under each video by connecting to a US server and scraping the content of the web page. 
Five types of information panels were found regarding climate change, COVID-19 Vaccine, COVID-19, U.S. elections and vaccination information, as shown in figure \ref{youtube_panel_screenshots}.

\begin{figure}[h]
	\centering
		\includegraphics[scale=0.3]{./img/youtube_panels/yt_1.png} 
		\includegraphics[scale=0.29]{./img/youtube_panels/yt_2.png} 
		\includegraphics[scale=0.294]{./img/youtube_panels/yt_3.png}
		\includegraphics[scale=0.305]{./img/youtube_panels/yt_4.png} 
		\includegraphics[scale=0.193]{./img/youtube_panels/yt_5.png} 
	\caption{Examples of YouTube information panels displayed under Youtube videos respectively about: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{Climate change}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{COVID-19 Vaccine}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{COVID-19}, \href{https://www.youtube.com/watch?v=8PAwc8nlE\_Q}{US elections} and \href{https://www.youtube.com/watch?v=OuQYMjpCwfU}{vaccination information}. The videos were accessed on July 21, 2021 from a US server.}
	\label{youtube_panel_screenshots}
\end{figure}

\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multicolumn{6}{|c|}{$170$ YouTube videos marked as false or inaccurate}                                                                                                                                                                                                                                                                                                                           \\ \hline
\makecell{Without \\ any \\ panel} & 
\makecell{With a \\ `COVID-19' \\ panel} & 
\makecell{With a \\ `COVID-19 \\ vaccine' panel} &
\makecell{With a \\ `climate change' \\ panel} &
\makecell{With a \\ `U.S. elections' \\ panel} &
\makecell{With a \\ `vaccination \\ information' panel}  
\\ \hline
\makecell{74 \\ (44 \%)} &
\makecell{71 \\ (42 \%)} &
\makecell{19 \\ (11 \%)} &
\makecell{4 \\ (2 \%)} &
\makecell{1 \\ (0.5 \%)} &
\makecell{1 \\ (0.5 \%)}
\\ \hline
\end{tabular}
\caption{Summary of the number of YouTube videos wich contain a certain information panel, among the set of videos marked as false or inaccurate by Science Feedback.}
\label{youtube_panel_proportions}
\end{table}
